Resilience and Home-Space for WSTS \thanks{This work was partly done while the authors were supported by the Agence Nationale de la Recherche grant BraVAS (ANR-17-CE40-0028).}

### 2023-10-26 VMCAI-revised-version/final.tex
up

We have omitted proofs for Lemma~\ref{downward compatible} and Lemma~\ref{Lemma intersection}
up until now
\mathieu{mettre ici les preuves suivantes (?): lemme1, et lemme 2}

@@

Additionnally ...

>>>>

We have omitted proofs for Lemma~\ref{downward compatible} and Lemma~\ref{Lemma intersection}
up until now since these are fairly straightforward technical proofs.
% \mathieu{mettre ici les preuves suivantes (?): lemme1, et lemme 2}
We provide now both. \\

@@

% Additionnally ...
